---
title: "FARS_for_NHTS"
author: "Borui Li"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{FARS_for_NHTS}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Package Description

`fars` package reads and map Fatality Analysis Reporting System (FARS) data for states in US 
from the [National Highway Traffic Safety 
Administration](https://www.nhtsa.gov/research-data/fatality-analysis-reporting-system-fars).

[FARS](https://en.wikipedia.org/wiki/Fatality_Analysis_Reporting_System) is using data from the US National Highway Traffic Safety Administration's Fatality Analysis Reporting System, which is a nationwide census providing the American public yearly data regarding fatal injuries suffered in motor vehicle traffic crashes. 



## Load Packages

```{r, echo=FALSE, message=FALSE}
library(fars)
library(maps)
library(dplyr)
```



## datafiles

Datafiles in the package are:

```{r}
list.files(system.file("extdata", package = "fars"))
```


## Package Functions

### Function `fars_read`

read in a data file as a tibble named "data":

```{r,eval=FALSE}
dat<-fars_read("accident_2013.csv.bz2")
```


### Function `make_filename`

Make the filename like "accident_2013.csv.bz2", depend on the year.

```{r,eval=FALSE}
make_filename(2013)
```


### Function `fars_read_years`


```{r}
fars_read_years(2013)
```


### Function `fars_summarize_years`

Summarizes yearly accidents data, by month.

```{r,eval=FALSE}
plot(fars_summarize_years(2015))
fars_summarize_years(c(2015, 2014))
```


### Function `fars_map_state`

The function displays a state map plot showing the distribution.
The state.num is between 1 to 56.

```{r,eval=FALSE}
fars_map_state(34,2013)
```


# Links:
* [Package fars GitHub](https://github.com/EnriquePH/FARS)
* [Package fars Travis CI](https://travis-ci.org/EnriquePH/FARS)
* [Package Appveyor](https://ci.appveyor.com/project/EnriquePH/FARS)
